A Spiking Independent Accumulator Model for Winner-Take-All

### 2017-01-24 doc/paper/paper.tex
Fix chktex warnings.

\subsection{Independent accumulator model}
The other WTA mechanism that we investigate is our proposed independent accumulator (IA) model.
We use the term `independent' to refer to the fact that there are no direct interactions between each accumulator, unlike in the LCA model which has direct competition between states.
To enable a form of competition, we add a second thresholding layer that  projects back to self-excite and mutually-inhibit the first layer.
We now provide the details of each layer, again implemented with the principles of the NEF.
\todo{Network diagram?}

@@

We now describe a number of metrics that will be calculated on the subset of trials that contain a clear decision.
% The time it takes to form a decision can be relevant too.
It is important to consider the speed at which the network can make decisions.
We therefore define the `decision time' as the length of time it takes to fulfil the conditions of a clear decision.
%These metrics cover the basic performance of the WTA mechanisms.
Likewise, when using a WTA mechanism within larger cognitive models, the exact magnitude of the outputs can be important.
Ideally, the output would be one for the winner and zero for all other outputs.\footnote{Technically, the winner output could be scaled to any magnitude.
We use $1$ for convenience.}
\todo{Have you tried decoding a threshold (say $\Theta(x_i - 0.15)$) off the LCA network?}
The LCA dynamics, however, prescribe an output of $u$ for the winner, with $u$ being the largest input.
We define the `winner error' $E_1$ as the difference of the winner output from $u$ for the LCA network, as the difference from one for the IA network and, for both models, the `runner-up error' $E_2$ as the difference of second largest output from zero (with negative values treated as zero).
We use the average output values over the time interval $(\SI{1}{\second}, \SI{2}{\second}]$ to calculate these error values (since these values fluctuate over time).
These two metrics only consider the final output averaged over time, but the model can produce transient outputs before the final decision is achieved.
Within the context of a larger model, this can be a problem as the transient output could be prematurely interpreted as a decision.
Thus, we define $E_{2,\max}$ as the `highest output of a losing choice' during the whole simulation.

>>>>

\subsection{Independent accumulator model}
The other WTA mechanism that we investigate is our proposed independent accumulator (IA) model.
We use the term `independent' to refer to the fact that there are no direct interactions between each accumulator, unlike in the LCA model which has direct competition between states.
To enable a form of competition, we add a second thresholding layer that  projects back to self-excite and mutually-inhibit the first layer.
We now provide the details of each layer, again implemented with the principles of the NEF\@.
\todo{Network diagram?}

@@

We now describe a number of metrics that will be calculated on the subset of trials that contain a clear decision.
% The time it takes to form a decision can be relevant too.
It is important to consider the speed at which the network can make decisions.
We therefore define the `decision time' as the length of time it takes to fulfil the conditions of a clear decision.
%These metrics cover the basic performance of the WTA mechanisms.
Likewise, when using a WTA mechanism within larger cognitive models, the exact magnitude of the outputs can be important.
Ideally, the output would be one for the winner and zero for all other outputs.\footnote{Technically, the winner output could be scaled to any magnitude.
We use $1$ for convenience.}
\todo{Have you tried decoding a threshold (say $\Theta(x_i - 0.15)$) off the LCA network?}
The LCA dynamics, however, prescribe an output of $u$ for the winner, with $u$ being the largest input.
We define the `winner error' $E_1$ as the difference of the winner output from $u$ for the LCA network, as the difference from one for the IA network and, for both models, the `runner-up error' $E_2$ as the difference of second largest output from zero (with negative values treated as zero).
We use the average output values over the time interval $(\SI{1}{\second}, \SI{2}{\second}]$ to calculate these error values (since these values fluctuate over time).  % chktex 9
These two metrics only consider the final output averaged over time, but the model can produce transient outputs before the final decision is achieved.
Within the context of a larger model, this can be a problem as the transient output could be prematurely interpreted as a decision.
Thus, we define $E_{2,\max}$ as the `highest output of a losing choice' during the whole simulation.
